Unbiased pangenome graphs

### 2022-09-14 manuscript/main.tex
ok

Although this particular study focuses on only a single small eukaryotic chromosome, it reveals that our basic understanding of reference bias in thes graph construction methods is correct.
By design, progressive pangenome graph construction methods will be affected by input genome order.
But, other symmetric methods avoid order bias.
%This leads to difficulty in building and designing pangenomes that is avoided by unbiased methods.

>>>>

Although this particular study focuses on only a single small eukaryotic chromosome, it reveals that our basic understanding of reference bias in these graph construction methods is correct.
By design, progressive pangenome graph construction methods will be affected by input genome order.
But, other symmetric methods avoid order bias.
%This leads to difficulty in building and designing pangenomes that is avoided by unbiased methods.
